---
title: "Bishkek"
author: "Muniza"
date: "`r Sys.Date()`"
output: html_document
---

```

## Including Plots





```{r}
# Load required libraries
library(readxl)
library(plotly)

# Load the data from Excel
data <- read_excel("C:/Users/UCA/Documents/summers 2023/IWPR internship/building/Final Project/Bishkek_data.xlsx")

# Set positions and dimensions for bars
xpos <- seq_len(nrow(data))
ypos <- data$`No. of Buildings`
dz <- data$`No. of Floors`

# Define a color map and normalize the number of floors to map to colors
light_blue <- c(0, 93, 138)  # (R, G, B) for light blue
color <- rgb(light_blue[1], light_blue[2], light_blue[3], maxColorValue = 255)  # Normalize RGB values to be in the range [0, 1]


```


```{r}
# Create the 3D bar trace
trace <- list(
  type = "scatter3d",
  x = xpos,
  y = ypos,
  z = rep(0, length(xpos)),
  mode = "markers",
  marker = list(
    color = dz,
    colorscale = list(
      c(0, "white"),
      c(5/max(dz), color),
      c(1, color)
    ),
    cmin = 0,
    cmax = max(dz),
    size = 1000
  )
)

# Create the layout for the 3D plot
layout <- list(
  title = "Bishkek",
  scene = list(
    xaxis = list(title = "Bishkek"),
    yaxis = list(title = "No. of Buildings"),
    zaxis = list(title = "No. of Floors")
  )
)

# Create the Plotly figure
fig <- plot_ly(data = trace, type = "scatter3d", mode = "markers", marker = marker, layout = layout)

# Show the plot
fig

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
